\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-01-15 papers/methods/paper.tex
Paper updates

We tested two models against simulated supernova sets; $\beta(c) = \beta_0 + \beta_1 c$ and $\beta(z) = \beta_0 + \beta_1 z$. See Section \ref{sec:simdes} for details on simulation generation. We found for both models that non-zero values for $\beta_1$ are preferred (even with constant $\beta$ used in simulation) due to severe degeneracy with selection effects. This degeneracy resulted in a significant bias in cosmology, and so in our final model we continue to adopt the constant $\alpha$ and $\beta$ found in traditional analyses.

@@

It is now well known that host galaxy environment has a significant effect on supernova properties. The latest sample of over 1300 spectroscopically confirmed Type Ia supernova show $>5\sigma$ evidence for correlation between host mass and luminosity \citep{Uddin2017}. The traditional correction, as employed in analyses such as \citet{Suzuki2012} and \citet{Betoule2014} invoke a step function such that $\Delta M = 0.08 \mathcal{H}(log(M) - 10))$, where $\mathcal{H}$ is the Heaviside step function and $M$ is the galaxy mass in solar masses. The scale of this step function varies from analysis to analysis, with the 0.08 value shown previously sourced from \cite{Sullivan2010} and used in \citet{Betoule2014}. In this work we adopt the model used in {\rubin}, which follows the work from \citet{Rigault2013}, such that we introduce two parameters to incorporate a redshift-dependent host galaxy mass correction:
\begin{equation}
\Delta M = \delta(0) \left[ \frac{1.9\left(1 - \frac{\delta(0)}{\delta(\infty)}\right)  }{0.9 + 10^{0.95z}} + \frac{\delta(0)}{\delta(\infty)}\right]
\end{equation}
We also take flat priors on the parameterisation $\delta(0)$, $\delta(0)/\delta(\infty)$.

@@

This method of adjusting the observed summary statistics is used throughout the traditional and BHM analyses, however it is normally constrained to band systematics. That is, each band for each survey has two systematics associated with it - the calibration uncertainty and the filter wavelength uncertainty. We include these in our approach, in addition to including HST Calspec calibration uncertainty, 10 SALT2 model systematic uncertainties, three dust systematics (scale, dust model, and transfer law) and also the systematic peculiar velocity uncertainty. This gives fourteen global systematics shared by all surveys, plus two systematics per band in each survey.

>>>>

We tested two models against simulated supernova sets; $\beta(c) = \beta_0 + \beta_1 c$ and $\beta(z) = \beta_0 + \beta_1 z$. See Section \ref{sec:simdes} for details on simulation generation. We found for both models that non-zero values for $\beta_1$ are preferred (even with constant $\beta$ used in simulation) due to severe degeneracy with selection effects. This degeneracy resulted in a significant bias in recovered cosmology, and so in our final model we continue to adopt the constant $\alpha$ and $\beta$ found in traditional analyses.

@@

It is now well known that host galaxy environment has a significant effect on supernova properties. The latest sample of over 1300 spectroscopically confirmed Type Ia supernovae show $>5\sigma$ evidence for correlation between host mass and luminosity \citep{Uddin2017}. The traditional correction, as employed in analyses such as \citet{Suzuki2012} and \citet{Betoule2014} invoke a step function such that $\Delta M = 0.08 \mathcal{H}(log(M) - 10))$, where $\mathcal{H}$ is the Heaviside step function and $M$ is the galaxy mass in solar masses. The scale of this step function varies from analysis to analysis, with the 0.08 value shown previously sourced from \cite{Sullivan2010} and used in \citet{Betoule2014}. In this work we adopt the model used in {\rubin}, which follows the work from \citet{Rigault2013}, such that we introduce two parameters to incorporate a redshift-dependent host galaxy mass correction:
\begin{equation}
\Delta M = \delta(0) \left[ \frac{1.9\left(1 - \frac{\delta(0)}{\delta(\infty)}\right)  }{0.9 + 10^{0.95z}} + \frac{\delta(0)}{\delta(\infty)}\right]
\end{equation}
We also take flat priors on the parameterisation $\delta(0)$, $\delta(0)/\delta(\infty)$.

@@

This method of adjusting the observed summary statistics is used throughout the traditional and BHM analyses, however it is normally constrained to band systematics. That is, each band for each survey has two systematics associated with it - the calibration uncertainty and the filter wavelength uncertainty. We include these in our approach, in addition to including HST Calspec calibration uncertainty, 10 SALT2 model systematic uncertainties, a dust systematic, a global redshift bias systematic and also the systematic peculiar velocity uncertainty. This gives thirteen global systematics shared by all surveys, plus two systematics per band in each survey.
